---
title: "BankChurners Report"
author: "Wuji Shan"
date: "12/10/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(cowplot)
library(scales)
library(lme4)
library(lmerTest)
library(purrr)
library(ggpubr)
library(correlationfunnel)
library(caret)
library(mlbench)
library(rsample)
library(forcats)
library(ggsci)
library(ggridges)
library(arm)
library(rstanarm)
library(kableExtra)
library(ggalluvial)
```

```{r, echo = FALSE}
source("functions.R")
```

# Abstract

Credit card has taken up a significant part of people's lives in the current society. The "Credit Card Customers" dataset is data of the consumer credit card portfolio of a bank, including 10,000 customers with their age, gender, income, marital status, education level, and etc. The manager wants to know the reason behind customer attrition. 

This report aims to deal with this customer attrition problem. I made exploratory data analysis and built a multilevel model, which uses utilizing Education_Level as the varying intercept and Gender as the varying slope. This report are consisted of 5 main parts: Introduction, Method, Result, Discussion, and Limitation. Other explorations besides what in Method part are all put in Appendix.

# Introduction

Customer churning is a serious situation faced by many corporations and organizations. It has become a significant point that how to deal with this issue and keep customers. To achieve that goal, one of the main focuses of corporations may be detecting the reasons why customers have made the churning decision via analyzing past data, so that they could take effective actions to prevent the customer leaving situation better.

The dataset I choose for this project is published on [Kaggle: Credit Card customers -- BankChurners Dataset](https://www.kaggle.com/sakshigoyal7/credit-card-customers), which includes 10127 observations and 23 variables. After data cleaning and processing, I will make exploratory data analysis from various angles, and use a multilevel model to see what and how attributes may influence the choice of customers to churn from the bank credit card service.

# Method

## Data Cleaning and Processing

```{r, echo = FALSE}
BankChurners <- read.csv("BankChurners.csv", header = TRUE)
BankChurners <- na.omit(BankChurners)

BankChurners <- BankChurners[, -c(1, 5, 10, 13:23)]

BankChurners <- BankChurners %>% filter(Education_Level != "Unknown" & 
                                          Marital_Status != "Unknown" & Income_Category != "Unknown")
```

```{r, echo = FALSE}
# Factor all categorical variables
BankChurners$Attrition_Flag <- as_factor(BankChurners$Attrition_Flag)
BankChurners$Gender <- as_factor(BankChurners$Gender)
BankChurners$Education_Level <- as_factor(BankChurners$Education_Level)
BankChurners$Marital_Status <- as_factor(BankChurners$Marital_Status)
BankChurners$Income_Category <- as_factor(BankChurners$Income_Category)
BankChurners$Card_Category<- as_factor(BankChurners$Card_Category)
```

```{r, echo = FALSE}
Existing <- subset(BankChurners, Attrition_Flag == "Existing Customer")
Attrited <- subset(BankChurners, Attrition_Flag == "Attrited Customer")
```


After looking into the data, I have finished the following processing steps to prepare for the next step of EDA and model fitting:  

1. Subset down to 8 variables and factor all categorical variables;  
2. Removed customer observations with "unknown" answer of categorical variables;  
3. Split the data into 2 groups based on customer type: Existing and Attrited Customer.  

After my data cleaning and processing, the data set utilized later has 7081 observations and 10 variables besides customer type.  


## Exploratory Data Analysis

```{r, echo = FALSE}
sum_Existing <- Existing %>% select_if(is.character) %>% map( ~ table(.) %>% prop.table())
sum_Attrited <- Attrited %>% select_if(is.character) %>% map( ~ table(.) %>% prop.table())
```

### Correlation Analysis

To find which and how features affect customer attrition, first, I'm interested in detecting the overall relationship between variables and the attrition flag of existing & attrited customer group after subseting down the data set. Here, I choose to plot a correlation funnel graph to show whether they are correlated with attrition. Three of variables chosen are numerical, and five of them are categorical.

```{r, echo = FALSE, warning = FALSE, fig.cap = "correlation analysis", fig.height = 4, fig.width = 10}
correlation <- BankChurners %>% binarize()

correlation %>%
  correlate(target = Attrition_Flag__Attrited_Customer) %>%
  filter(feature %in% c("Customer_Age", "Total_Relationship_Count", "Months_Inactive_12_mon", "Gender", 
                        "Education_Level", "Income_Category", "Marital_Status", "Card_Category")) %>%
  plot_correlation_funnel(interactive = FALSE, limits = c(-0.3, 0.3))
```

Via investigating these 8 variables as a correlation funnel graph, we can observe the order of their importance to churning options is from the top to bottom. x-axis going larger than 0 represents that the variable type is more likely to make the choice of attrition; on the contrary, x-axis smaller than 0 represents that they are more likely to exist.  

### Level of Total Relationship Count & Inactivity

Inactive months and total relationship count are the top 2 variables in the correlation funnel, so I want to investigate them to prepare for the comparison of visualization and model fitting.
```{r, echo = FALSE}
products <- BankChurners %>% 
  dplyr::select(Attrition_Flag, Total_Relationship_Count)

# Levels of Inactivity by attrition flag
plot_products <- products %>% 
  ggplot(aes(x = Total_Relationship_Count, y = Attrition_Flag, fill = Attrition_Flag)) + 
  stat_density_ridges(quantile_lines = TRUE, quantiles = 2, alpha = 0.4) + 
  scale_fill_nejm() + 
  labs(
    title = "Level of Total Relationship Count",
    x = "Total Relationship Count (number of products held)", 
    y = "Group"
  )

activity <- BankChurners %>% 
  dplyr::select(Attrition_Flag, Months_Inactive_12_mon)

# Levels of Inactivity by attrition flag
plot_activity <- activity %>% 
  ggplot(aes(x = Months_Inactive_12_mon, y = Attrition_Flag, fill = Attrition_Flag)) + 
  stat_density_ridges(quantile_lines = TRUE, quantiles = 2, alpha = 0.4) + 
  scale_fill_nejm() + 
  labs(
    title = "Level of Inactivity",
    x = "Inactive Months", 
    y = "Group"
  )
```

```{r, echo = FALSE, message = FALSE, fig.cap = "Level of Total Relationship Count & Inactivity", fig.height = 3, fig.width = 10}
ggarrange(plot_products, plot_activity, ncol = 2, nrow = 1)
```

These 2 plots in figure 3 shows that Attrition Customers have lower relationship count (products held) and higher levels of Inactivity.

### Education Level & Income category

Education level and income category are the top 2 categorical variables besides gender in the correlation funnel, so I want to investigate them to prepare for the comparison of visualization and model fitting. Also, I will explore relationship between combination of various variables including these two and the attrition choice.
```{r, echo = FALSE}
# Assign the level order
Education_Level <- c("College", "Doctorate", "Graduate", "High School", "Post-Graduate", "Uneducated")

# Find % of customers who are about to leave
education <- BankChurners %>%
  dplyr::select(Attrition_Flag, Education_Level) %>% 
  count(Attrition_Flag, Education_Level) %>% 
  group_by(Education_Level) %>% 
  mutate(percent = n / sum(n)) %>% 
  ungroup() %>% 
  arrange(desc(percent)) %>% 
  mutate(
    PERCENT = scales::percent(percent),
    Education_Level = Education_Level %>% factor(levels = c("College", "Doctorate", "Graduate", "High School", "Post-Graduate", "Uneducated")) %>% fct_rev(),
    Education_Level = Education_Level %>% as_factor() %>% fct_reorder(percent),
    Attrition_Flag = Attrition_Flag %>% as_factor() %>% fct_rev()
  ) 
```

```{r, echo = FALSE}
# Plot Visualization
plot_education<-
  education %>% 
  ggplot(aes(x = Education_Level, y = percent, color= Attrition_Flag)) + 
  geom_segment(aes(yend = 0, xend = Education_Level), size = 1) + 
  geom_point() + geom_label(aes(label = PERCENT), hjust = "inward",
                            size = 3) + coord_flip() +
  facet_wrap(~ Attrition_Flag) + 
  theme(legend.position = "none") + 
  scale_colour_nejm() + 
  labs(
    title = "Levels of Attrition by Education Level",
    x = "Education Level",
    y = "Attrition Percentage"
  )
```

```{r, echo = FALSE}
# Assign the level order
income_level <- c("$120K +", "$40K - $60K", "$80K - $120K", 
                  "$60K - $80K", "Less than $40K")

# Find % of customers who are about to leave
income <- BankChurners %>%
  dplyr::select(Attrition_Flag, Income_Category) %>% 
  count(Attrition_Flag, Income_Category) %>% 
  group_by(Income_Category) %>% 
  mutate(percent = n / sum(n)) %>% 
  ungroup() %>% 
  arrange(desc(percent)) %>% 
  mutate(
    PERCENT = scales::percent(percent),
    Income_Category = Income_Category %>% factor(levels = c("$120K +", "$40K - $60K", "$80K - $120K", 
                  "$60K - $80K", "Less than $40K")) %>% fct_rev(),
    Income_Category = Income_Category %>% as_factor() %>% fct_reorder(percent),
    Attrition_Flag = Attrition_Flag %>% as_factor() %>% fct_rev()
  ) 
```

```{r, echo = FALSE}
# Plot Visualization
plot_income <- 
  income %>% 
  ggplot(aes(x = Income_Category, y = percent, color= Attrition_Flag)) + 
  geom_segment(aes(yend = 0, xend = Income_Category), size = 1) + 
  geom_point() + geom_label(aes(label = PERCENT), hjust = "inward",
                            size = 3) + coord_flip() +
  facet_wrap(~ Attrition_Flag) + 
  theme(legend.position = "none") + 
  scale_colour_nejm() + 
  labs(
    title = "Levels of Attrition by Income Category",
    x = "Income Category",
    y = "Attrition Percentage"
  )
```

```{r, echo = FALSE, message = FALSE, fig.cap = "Education & Income Proportion Analysis", fig.height = 3, fig.width = 10}
ggarrange(plot_education, plot_income, ncol = 2, nrow = 1)
```

We can observe that the highest Education Level Doctorate has a highest proportion among attrition customers. The lowest proportion group is high school level, which takes up lower proportion than uneducated level. Also, we can observe that the highest income category 120K+ dollars has a highest proportion among attrition customer group. followed by Less than 40K dollars, which is the lowest income category. 

### Customer Attrition Combination

After investigating individual variable, I'm wondering whether I can find a combination of variables which are more likely to make churning options. From Figure 1, we can see that Gender, Education_Levl, and Income_Category are three categorical variables having largest correlation, so we choose to first combine them.

```{r, echo = FALSE}
combination <- BankChurners %>% 
  dplyr::select(Attrition_Flag, Gender, Education_Level, Income_Category) %>% 
  filter(Attrition_Flag == "Attrited Customer") %>% 
  count(Attrition_Flag, Gender, Education_Level, Income_Category) %>% 
  mutate(
    com_group = ifelse(Gender == "F" & Education_Level == "Graduate" & 
                         Income_Category == "Less than $40K", "Yes", "no")
  )
```

```{r, echo = FALSE, fig.height = 3, fig.width = 10, fig.cap = "Detecting Combination of Group"}
combination %>% 
  ggplot(aes(y = n, axis1 = Gender, axis2 = Education_Level, axis3 = Income_Category)) +
  geom_alluvium(aes(fill = com_group), alpha = 0.4,  absolute = FALSE) + 
  geom_stratum(absolute = FALSE, width = 0.45) + 
  geom_text(stat = "stratum", aes(label = after_stat(stratum)), absolute = FALSE) + 
  scale_x_discrete(limits = c("Income Category", "Education Level", "Gender"), expand = c(.08, .05)) + 
  labs(title = "Detecting Combination of Groups -- Attrited Customer", y = "Count")
```
We can observe that Female Graduates in the low income category take up the most proportion of Attrited customer group.

## Model Fitting
```{r, echo = FALSE}
BankChurners$Attrition_Flag <- ifelse(BankChurners$Attrition_Flag == "Existing Customer", 0, 1)
```

I used a multilevel model to fit the data, utilizing Education_Level as the varying intercept and Gender as the varying slope. I have attempted several multilevel models to get better fitting, including ‘lmer’ and ‘glmer’ (which is in the appendix). Comparing their results, I finally chose ‘stan_glmer’ because the response of this data set is binary, which needs to use logistic methods.

```{r, include = FALSE}
fit_BankChurners <- stan_glmer(Attrition_Flag ~ Customer_Age + Marital_Status + Income_Category + 
                            Card_Category + Total_Relationship_Count + Months_Inactive_12_mon + 
                            (1 + Gender|Education_Level), data = BankChurners)
```

```{r}
# fit_BankChurners <- stan_glmer(Attrition_Flag ~ Customer_Age + Marital_Status + Income_Category + 
#                             Card_Category + Total_Relationship_Count + Months_Inactive_12_mon + 
#                             (1 + Gender|Education_Level), data = BankChurners)
```
The binned residual plot shows that ‘stan_glmer’ is a better model fit here as well, because most points fall inside the confidence bands, and there is not a distinctive pattern to the residuals. Additionally, I removed some variables which owns coefficients too small to identify and compare.

```{r, echo = FALSE, message = FALSE}
# summary(fit_BankChurners, digits = 4)
```

# Result
```{r, echo = FALSE}
Fixed_Effect <- fixef(fit_BankChurners)
Random_Effects <- round(ranef(fit_BankChurners)$Education_Level, 3)
```

## Model Coefficients
Because many variables are fit in the model, I only choose to take one example formula for card type category:  

$Attrition Flag = 0.0007 - 0.0253*(Gold Card) - 0.0059*(Silver Card) + 0.0483*(Platinum Card)$  

The coeffcient of Card_CategoryGold and Card_CategorySilver are both negative, but that of Card_CategoryPlatinum is positive, which represents that in average, customers owning gold or silver cards are more likely to stay but customers with platinum cards are more liekly to choose to churn from the bank's credit card service.

## Fixed Effects

|    Variable                  | Estimate | s.d.   |t value|
|:---:                         |:---:     |:---:   |:---:|
|Customer_Age                  |-0.0002   | 0.0005 |-0.434 | 
|Marital_StatusSingle          | 0.0136   | 0.0088 | 1.570 |
|Marital_StatusDivorced        | 0.0126   | 0.0159 | 0.812 |
|Income_CategoryLess than $40K | 0.0173   | 0.0187 | 0.656 |
|Income_Category$80K - $120K   | 0.0266   | 0.0148 | 1.784 |
|Income_Category$40K - $60K    | 0.0032   | 0.0168 |-0.053 |
|Income_Category$120K +        | 0.0452   | 0.0180 | 2.462 |
|Card_CategoryGold             |-0.0253   | 0.0399 |-0.641 |
|Card_CategorySilver           |-0.0059   | 0.0184 |-0.304 |
|Card_CategoryPlatinum         | 0.0483   | 0.1099 | 0.501 |
|Total_Relationship_Count      |-0.0344   | 0.0027 |-12.516 |
|Months_Inactive_12_mon        | 0.0558   | 0.0043 | 13.138 |

## Random Effects
```{r, echo = FALSE}
#print(Fixed_Effect)
Random_Effects <- data.frame(Random_Effects)
#print(Random_Effects)
#plot(fitted(fit_BankChurners), resid(fit_BankChurners))
```
|    Type                  | Intercept | GenderM
|:---:                     |:---:     |:---:  
|High School               |-0.007   | 0.008 
|Graduate                  |-0.009   | 0.032 
|Uneducated                |-0.002   | 0.008
|College                   | 0.001   |-0.002
|Post-Graduate             | 0.008   | 0.006
|Doctorate                 | 0.006   | 0.047  

# Discussion

From the fitting results of the multilevel model, we can see some variables types are statistically significant, including Income_Category$120K +, Total_Relationship_Count, and Months_Inactive_12_mon -- effects not that much but there exist. The model results are similar to what I've mentioned before in the first two parts of EDA - correlation analysis and level of Total Relationship Count & Inactivity, which are really top 2 important variables affecting response most both in the EDA and model fitting results. Most variables state positive impacts on attrition choice.

When it only comes to findings of this report, the bank could take some actions to prevent their customer attrition better. One is to put more efforts on lower income group. Although their average spending seems not much significant, their population amount takes up nearly 40% of all customers in this data set. The other is focusing on customers' activity level. We can observe that the longest inactive months of attrited customers is 6 months. During these 6 months, the bank can detect the customer's inactivity and take actions like calling to do market research, introduce new products, or invite them to bank's promotions to arouse consumers' interest.  

One interesting finding is both EDA and model results show that customers with platinum cards are more likely to leave the service. Platinum cards are generally related to customers with more products held and active transactions, which are both more correlated to existing customers, but card category of plstinum shows the contrary correlation, meaning that the results of customer churning situation may have been also affected by some other factors not included but worth being explored in the future analysis.  

# Limitation

Limitation of the model process is that the use of variables is not enough based on the whole number of 23 variables, because I only chose 8 of them to investigate. Also, there exist two variables Trans_Count_Amt and Trans_Count_Ct, which are really two most correlated variables when doing funnel analysis. However, each time I tried to add them into model fitting via 'glmer' and 'stan_glmer', the binned residual plot all shows a distinctly strange pattern and most of points fall outside the confidence bands. In the future analysis, I will add more features to do research and find better methods to make well-fitting model.

# Reference

1. Goyao, Sakshi, Credit Card customers, Kaggle,  
https://www.kaggle.com/sakshigoyal7/credit-card-customers

2. Introducing Correlation Funnel - Customer Churn Example,  
https://cran.r-project.org/web/packages/correlationfunnel/vignettes/introducing_correlation_funnel.html  

3. ggpubr: Publication Ready Plots, STHDA,  
http://www.sthda.com/english/articles/24-ggpubr-publication-ready-plots/81-ggplot2-easy-way-to-mix-multiple-graphs-on-the-same-page/  

4. Interpreting Residual Plots to Improve Your Regression, qualtrics  
https://www.qualtrics.com/support/stats-iq/analyses/regression-guides/interpreting-residual-plots-improve-regression/ 

5. Brunson, Jason Cory, Alluvial Plots in ggplot2, 2020.12.04,  
https://cran.r-project.org/web/packages/ggalluvial/vignettes/ggalluvial.html




\pagebreak

# Appendix

8 Variables Utilized:  

|    Variable              | Explanation
|:---:                     |:---:     |:---:  
|Customer_Age              | Customer's Age in Years
|Gender                    | M = Male, F = Female  
|Education_Level           | Educational Qualification of the account holder
|Marital_Status            | Married, Single, Divorced, Unknown
|Income_Category           | Annual Income Category of the account holder
|Card_Category             | Type of Card (Blue, Silver, Gold, Platinum)
|Total_Relationship_Count  | Total no. of products held by the customer
|Months_Inactive_12_mon    | Number of months inactive in the last 12 months

```{r, echo = FALSE}
sum_Churner <- BankChurners %>% select_if(is.character) %>% map( ~ table(.) %>% prop.table())
```

### Distributions of all numeric variables
```{r, echo = FALSE, fig.height = 3, fig.width = 10, fig.cap = "Distributions of all numeric variables"}
BankChurners %>% keep(is.numeric) %>%
  gather() %>% ggplot(mapping = aes(x = value, fill = key)) + geom_histogram() + 
  facet_wrap(~ key, scale = "free")
```

### binned residual plot for stan_glmer model
```{r, echo = FALSE, fig.align = "center"}
binnedplot(fitted(fit_BankChurners), resid(fit_BankChurners))
```

### Pie Charts of Attrition_Flag

```{r, echo = FALSE}
##### set pie for existing customers: Education
pie_existing_edu <- data.frame(class = c("College", "Doctorate", "Graduate", "High School", 
                                         "Post-Graduate", "Uneducated"), 
                               Prop = c(11.93, 4.74, 36.61, 23.73, 5.93, 17.06))
# Add label position
pie_existing_edu <- pie_existing_edu %>%
  arrange(desc(class)) %>%
  mutate(lab.ypos = cumsum(Prop) - 0.5*Prop)
# set colors
mycols_edu <- c("#bfcdd0", "#6e7d75", "#d0776e", "#ebbdb1", "#eaaa65", "#d6e66f")

##### set pie for attrited customers: Education
pie_attrited_edu <- data.frame(class = c("College", "Doctorate", "Graduate", "High School", 
                                         "Post-Graduate", "Uneducated"), 
                               Prop = c(11.86, 6.74, 36.48, 21.29, 6.92, 16.71))
# Add label position
pie_attrited_edu <- pie_attrited_edu %>%
  arrange(desc(class)) %>%
  mutate(lab.ypos = cumsum(Prop) - 0.5*Prop)
```

```{r, echo = FALSE, fig.cap = "Education Level Proportion Comparison", fig.height = 5, fig.width = 14}
plot_existing_edu <- 
  piechart(pie_existing_edu, "Existing Customer - Education Level", mycols_edu)

plot_attrited_edu <- 
  piechart(pie_attrited_edu, "Attrited Customer - Education Level", mycols_edu)

ggarrange(plot_existing_edu, plot_attrited_edu, ncol = 2, nrow = 1)
```

```{r, echo = FALSE}
##### set pie for existing customers: Marital Status
pie_existing_Marital <- data.frame(class = c("Divorced", "Married", "Single"), 
                               Prop = c(7.99, 50.85, 41.15))
# Add label position
pie_existing_Marital <- pie_existing_Marital %>%
  arrange(desc(class)) %>%
  mutate(lab.ypos = cumsum(Prop) - 0.5*Prop)
# set colors
mycols_Marital <- c("#bcc0ec", "#e7a5cc", "#f281a7")

##### set pie for attrited customers: Marital Status
pie_attrited_Marital <- data.frame(class = c("Divorced", "Married", "Single"), 
                               Prop = c(8.27, 47.53, 44.20))
# Add label position
pie_attrited_Marital <- pie_attrited_Marital %>%
  arrange(desc(class)) %>%
  mutate(lab.ypos = cumsum(Prop) - 0.5*Prop)
```

```{r, echo = FALSE, fig.cap = "Marital Status Proportion Comparison", fig.height = 5, fig.width = 14}
plot_existing_Marital <- 
  piechart(pie_existing_Marital, "Existing Customer - Marital Status", mycols_Marital)

plot_attrited_Marital <- 
  piechart(pie_attrited_Marital, "Attrited Customer - Marital Status", mycols_Marital)

ggarrange(plot_existing_Marital, plot_attrited_Marital, ncol = 2, nrow = 1)
```

```{r, echo = FALSE}
##### set pie for existing customers: Income Category
pie_existing_income <- data.frame(class = c("$120K +", "$40K - $60K", "$60K - $80K", 
                                            "$80K - $120K", "Less than $40K"), 
                               Prop = c(7.88, 20.24, 16.05, 16.97, 38.86))
# Add label position
pie_existing_income <- pie_existing_income %>%
  arrange(desc(class)) %>%
  mutate(lab.ypos = cumsum(Prop) - 0.5*Prop)
# set colors
mycols_income <- c("#94acbc", "#527b7c", "#cbacd9", "#8a7ba8", "#3ea4af")

##### set pie for attrited customers: income category
pie_attrited_income <- data.frame(class = c("$120K +", "$40K - $60K", "$60K - $80K", 
                                            "$80K - $120K", "Less than $40K"), 
                               Prop = c(9.16, 18.33, 13.03, 16.98, 42.50))
# Add label position
pie_attrited_income <- pie_attrited_income %>%
  arrange(desc(class)) %>%
  mutate(lab.ypos = cumsum(Prop) - 0.5*Prop)
```

```{r, echo = FALSE, fig.cap = "Income Category Proportion Comparison", fig.height = 5, fig.width = 14}
plot_existing_income <- 
  piechart(pie_existing_income, "Existing Customer - income category", mycols_income)

plot_attrited_income <- 
  piechart(pie_attrited_income, "Attrited Customer - income category", mycols_income)

ggarrange(plot_existing_income, plot_attrited_income, ncol = 2, nrow = 1)
```

```{r, echo = FALSE}
# Assign the card category level order
card_type <- c("Blue", "Gold", "Silver", "Platinum")

# Find % of customers who are about to leave
card <- BankChurners %>%
  dplyr::select(Attrition_Flag, Card_Category) %>% 
  count(Attrition_Flag, Card_Category) %>% 
  group_by(Card_Category) %>% 
  mutate(percent = n / sum(n)) %>% 
  ungroup() %>% 
  arrange(desc(percent)) %>% 
  mutate(
    PERCENT = scales::percent(percent),
    Card_Category = Card_Category %>% factor(levels = c("Blue", "Gold", "Silver", "Platinum")) %>% fct_rev(),
    Card_Category = Card_Category %>% as_factor() %>% fct_reorder(percent),
    Attrition_Flag = Attrition_Flag %>% as_factor() %>% fct_rev()
  ) 
```

```{r, echo = FALSE, fig.cap = "Income Category Proportion Analysis", fig.height = 5, fig.width = 14}
# Plot Visualization
card %>% 
  ggplot(aes(x = Card_Category, y = percent, color= Attrition_Flag)) + 
  geom_segment(aes(yend = 0, xend = Card_Category), size = 1) + 
  geom_point() + geom_label(aes(label = PERCENT), hjust = "inward",
                            size = 3) + coord_flip() +
  facet_wrap(~ Attrition_Flag) + 
  theme(legend.position = "none") + 
  scale_colour_nejm() + 
  labs(
    title = "Levels of Attrition by Card Category",
    x = "Card Category",
    y = "Attrition Percentage"
  )
```

### Model Fitting
```{r, warning = FALSE}
fit_BankChurners_glmer <- glmer(Attrition_Flag ~ Customer_Age + Marital_Status + Income_Category + 
                            Card_Category + Total_Relationship_Count + Months_Inactive_12_mon + 
                            (1 + Gender|Education_Level), 
                          data = BankChurners)
```

```{r, echo = FALSE}
summary(fit_BankChurners_glmer)
```

```{r, echo = FALSE}
Fixed_Effect_glmer <- round(fixef(fit_BankChurners_glmer)[1], 3)
Random_Effects_glmer <- round(ranef(fit_BankChurners_glmer)$Education_Level, 3)
```

```{r, echo = FALSE}
print(Fixed_Effect_glmer)
print(Random_Effects_glmer)
#plot(fitted(fit_BankChurners_glmer), resid(fit_BankChurners_glmer))
binnedplot(fitted(fit_BankChurners_glmer), resid(fit_BankChurners_glmer))
```